---
title: "Index"
author: "J. Kyle Wathen"
date: "5/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Platform Trial Simulator  

[![Coverage Status](https://img.shields.io/codecov/c/github/kwathen/PlatformTrialSimulator/master.svg)](https://codecov.io/github/kwathen/PlatformTrialSimulator?branch=master)
[![Travis-CI Build Status](https://travis-ci.org/kwathen/PlatformTrialSimulator.svg?branch=master)](https://travis-ci.org/kwathen/PlatformTrialSimulator)
 
## License 
This package is governed by the JRD Platform Trial Simulation License, which is the GNU General Public License V3 with additional terms. The precise license terms are located in [LICENSE](https://github.com/kwathen/PlatformTrialSimulatorP/blob/master/inst/LICENSE) and [GPL](https://github.com/kwathen/PlatformTrialSimulatorP/blob/master/inst/GPL).


## Introduction
This project is designed to help clinical trial designers simulate a platform trial.   This project is intended for simulation purposes only.  For the purposes of this project and R code base a platform trial is a clinical trial designed to accommodate multiple treatments or interventions added to the trial either at the beginning of the trial or any time thereafter.   Each intervention is added through an Intervention Specific Appendix (ISA).  Each ISA typically randomizes between placebo or control and one or more intervention doses (or combinations).  If trials for multiple interventions in the same disease area are considered, then a platform trial provides a unified framework for designing and running a single, multiple ISA, platform trial.  Potential benefits of a platform trial are shorter more efficient trials due to a single framework for multiple interventions and borrowing of placebo or control patients across ISAs thus reducing the overall number of patients treated with placebo/control.  

This package is under development and is working and has been used to simulate several trials.  As case studies are created they will be added to the Examples directory of the package to help users create the necessary structures.  The tar.gz files in this repository are included as testing versions for beta testers as new updates are added. 

Please follow this project to be notified of updates.   

## Installation 
Currently this package is not available on CRAN but may be installed direclty from the tar.gz files located in GitHub.  The most recent version is [Version 1.2.1.2](https://github.com/kwathen/PlatformTrialSimulator/blob/master/PlatformTrialSimulator_1.2.1.2.tar.gz).   If you have the  PlatformTrialSimulator_1.2.1.2.tar.gz in the current working directory the following command will install the package.

```{r, eval = FALSE}
install.packages("PlatformTrialSimulator_1.2.1.2.tar.gz", repos=NULL)
````

## Usage 
In the instillation folder there is an Examples directory that contains full examples. 
