---
title: "Examples"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Examples

Examples are included in the installation folder as case studies, CaseStudy2 and CaseStudy3 with corresponding R Studio project files. CaseStudy2.Rpoj and CaseStudy3.Rpoj   


## Case Study 2

# Description

Located in the Examples/CaseStudy2
Platform trial with 1 ISA.
1 interim analysis at when 30 patients have 24 weeks of follow-up
Final Analysis (FA) when all patients have the outcome observed.
30 patients on control 60 patients on treatment
Primary outcome is repeated measure evaluated at baseline, 4, 8, 12, 16, 20 and 24 weeks after treatment
Analyze difference from baseline at week 24 compared to control
Minimum Acceptable Value MAV = 0.5 difference between control and treatment
This is the minimum difference between treatment and control
( m24 - m0 )Cont – (m24 - m0 )Trt

# R Code
Begin with the BuildMe.R file.    This file loads the PlatformTrialSimulator package and sources the design file.  
The file TrialDesign.R contains the function necessary to set-up the design object.
The file SimulationDesign.R contains the functions necessary to set-up the simulation design. 

## Case Study 3
Located in the Examples/CaseStudy3
Platform trial with 1 ISA.
No  interim analysis
Final Analysis (FA) when all patients have the outcome observed.
30 patients on control 60 patients on treatment
Assume same design as Case Study 2
No need to modify the TrialDesign.R file
Assume that patients either respond (R) or they are non-responder NR
If a patient is a responder (R) their outcomes are generated from mean vector 2
If a patient is a non-responder (NR) their outcomes are generated from mean vector 1
Utilize SimPatientOutcomes.MVNWithCovariate outcome type
Historical data suggests that 2% of patients on control will respond.
Treatment should increase the % of responders.


# R Code
Begin with the BuildMe.R file.    This file loads the PlatformTrialSimulator package and sources the design file.  
The file TrialDesign.R contains the function necessary to set-up the design object.
The file SimulationDesign.R contains the functions necessary to set-up the simulation design. 

```{r pressure, echo=FALSE}
plot(pressure)
```
