---
title: "OCTOPUS General Workflow"
author: "J. Kyle Wathen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OCTOPUS General Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# OCTOPUS General Workflow

Simulating a platform trial requires many details to be specified.   In general, once OCTOPUS is installed the user will create a new project with project specific files that will build the required structures and run the simulations.  This section walks through the general steps involved to go from having OCTOPUS installed to running your first simulation.  

To illustrate the typically workflow, an example is walked through in the next steps.

Example Platform Trial
  * 3 ISAs, each with experimental treatment and the same control
  * ISA 1 - 50 patients on control, 100 experimental, ISA 2&3 - 25 patients on control, 125 on experimental treatment
  * ISA 1 is open at the start of the trial, ISA 2 will open at month 6, ISA 3 will open at month 12
  * Primary outcome is binary
  * Use a Bayesian Beta Binomial model

For this example, assume that the analysis and binary outcome is not part of OCTOPUS and are new functions for this hypothetical example. 

## Step 1 - Create Project

At the start of a project you will typically make a call to [OCTOPUS::CreateProject](../reference/CreateProject.html) with some initial information about the trial you are trying to simulate.  The CreateProject-XXX files in the [OCTOPUS-Examples Repo](https://github.com/kwathen/OCTOPUS-Examples) are very helpful.    

Example of a CreateProject.R file.

```{r setp, eval=FALSE}
library( OCTOPUS )
strProjDir                 <- ""   # Since this is not a complete path, directory is created relative to working directory when this file is executed
strProjName                <- "ThreeISA"
strAnalysis                <- "BetaBinomial"
strSimPatOutcome           <- "Binary"
strBorrowing               <- "AllControls"

# The matrix  mQtyPats contains the number of patients in each arm in each ISA.  Each row represents an ISA, each column is
# a treatment with the first column the number of patients in control.  The first ISA (row 1) has 50 patients on control
# 100 on treatment 2.  The second ISA (row 2) has 25 patients on control and 125 on treatment 2
# the third ISA has 25 on control and 125 on treatment.  
mQtyPats                   <- matrix( c( 50, 100,
                                         25, 125,
                                         25, 125), byrow=TRUE, ncol=2 )
dQtyMonthsFU               <- 6
bCreateProjectSubdirectory <- TRUE
nQtyReps                   <- 250
vISAStartTimes             <- c( 0, 6, 12  )

strResult <- CreateProject( strProjectDirectory        = strProjDir,
                            strProjectName             = strProjName,
                            strAnalysisName            = strAnalysis,
                            strSimPatientOutcomeName   = strSimPatOutcome,
                            strBorrowing               = strBorrowing,
                            nQtyReps                   = nQtyReps,
                            mQtyPatientsPerArm         = mQtyPats,
                            dQtyMonthsFU               = dQtyMonthsFU,
                            vISAStartTimes             = vISAStartTimes,
                            bCreateProjectSubdirectory = bCreateProjectSubdirectory)

cat( strResult)

```
